Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-21 paper/Draft.tex
Some outoutlines of the discussions about the graphs. hist of revision needs to made.

Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty. While in fact, we observe long-lasting heterogeneity in uncertainty both from professional forecasters and households. Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e. disagreements, but alslo great heterogeneity in uncertainty. One stylized fact from these observations is that that the dispersion in ucnertainty seems consistent over time.

>>>>

The left  three figures look into the relationship between forecast error and uncertainty. In general, one may expect that  greater ex ante uncertainty implies greater ex post forecast errors.

Many literature use disagreements and uncertainty interchangably but they are different objects. From the graph, we can also see in general uncertainty captures different information from disagreements. This is more so in professional forecaster data. There is a more obvious correlation between disgreements and uncertainty.

Once implication from FIRE is that all individuals not only agree on mean but also share same degree of uncertainty. While in fact, we observe long-lasting heterogeneity in uncertainty both from professional forecasters and households. Figure \ref{IQR_Unceratitny} show that there is  not only dispersion of individual forecasts i.e. disagreements, but alslo notable heterogeneity in uncertainty. One stylized fact from these observations is that  the dispersion in ucnertainty seems persistent over time.
